Geometric Control for Autonomous Landing on Asteroids

### 2017-08-09 manuscript.tex
Add some discussion of image processing

Concurrent with the simulation, we generate images of Itokawa using Blender, as described earlier.
The images are generated at a rate of \SI{1}{\hertz} and stored for post processing and one exampel view is shown in~\cref{fig:example_image}. 
From these images we estimate the position of the camera relative to the asteroid using monocular localization.
In this work, we demonstrate the ability to generate realistic imagery and the processing of these images to determine a state estimate of the camera pose.
In future work, we seek to use this state estimate in a closed-loop controller to enable a fully-autonomous control system for the spacecraft. 
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/test000837.png}
    \caption{Example image of Itokawa at \( t = \SI{837}{\second}\)\label{fig:example_image}}
\end{figure}
From each image, a series of features are detected and tracked between subsequent frames.
A visualization of this process is shown in~c\ref{fig:orbslam_mappoints} which shows the tracked features of the image in green.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth, keepaspectratio]{figures/orbslam_mappoints.png}
    \caption{ORB-SLAM2 Feature Tracking Visualization\label{fig:orbslam_mappoints}}
\end{figure}
% TODO: Plots of trajectory

>>>>

Concurrent with the simulation, we generate images of Itokawa using Blender, as described earlier.
The images are generated at a rate of \SI{1}{\hertz} and stored for post processing and one exampel view is shown in~\cref{fig:example_image}. 
From these images we estimate the position of the camera relative to the asteroid using monocular localization.
In this work, we demonstrate the ability to generate realistic imagery and the processing of these images to determine a state estimate of the camera pose.
In future work, we seek to use this state estimate in a closed-loop controller to enable a fully-autonomous control system for the spacecraft. 
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/test000837.png}
    \caption{Example image of Itokawa at \( t = \SI{837}{\second}\)\label{fig:example_image}}
\end{figure}
From each image, a series of features are detected and tracked between subsequent frames.
A visualization of this process is shown in~\cref{fig:orbslam_mappoints} which shows the tracked features of the image in green.
From these tracked features it is possible to estimate the relative motion of the camera~\cite{szeliski2010}.
\Cref{fig:orbslam_localization} shows a visualization of the localization process from the imagery. 
\begin{figure}[htbp]
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/orbslam_mappoints.png} 
        \caption{ORB-SLAM2 Feature Tracking Visualization\label{fig:orbslam_mappoints}} 
    \end{subfigure}~
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/orbslam_localization.png} 
        \caption{ORB-SLAM2 Localization from monocular images \label{fig:orbslam_localization}} 
    \end{subfigure} 
\end{figure}
% TODO: Plots of trajectory
